---
output:
  pdf_document: default
---
#Required packages

```{r}
library(gtrendsR)
library(tidyverse)
library(data.table)
library(anytime)
library(tibbletime)
library(fastDummies)
library(lubridate)
library(scales)
library(mudata2)
library(lme4)
```



#VoterData preparation

Import and wrangling
```{r}
library(readxl)
VoterDat<- read_excel("Voter turnout data/idea_export_40_5edfe09b20bc6.xls")


#Remove all observations that are not from 2014 and 2019 as well as unecessesary variables (columns)
VoterDat1419 <- VoterDat %>% 
  filter(Year > 2013) %>% 
  select(Country, Year, `Voter Turnout`, `Total vote`, Population)
```


Transforming three columns to numeric
```{r} 

VoterDat1419$Population <- as.numeric(gsub(",","",VoterDat1419$Population))
VoterDat1419$'Total vote' <- as.numeric(gsub(",","",VoterDat1419$'Total vote'))
VoterDat1419$`Voter Turnout` <- as.numeric(gsub("%", "", VoterDat1419$`Voter Turnout`))

```

#Gtrends data import and wrangling

Import of the needed gtrends objects.

```{r}
#Austria
AT14 <- gtrends(c("die europäische union", "europawahl", "europäisches parlament"), geo = "AT", time = "2014-04-25 2014-05-25", low_search_volume =T)
AT19 <- gtrends(c("die europäische union", "europawahl", "europäisches parlament"), geo = "AT", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Croatia
HR14 <- gtrends(c("europska unija", "izbori za evropski parlament", "europski parlament"), geo = "HR", time = "2014-04-25 2014-05-25", low_search_volume =T)
HR19 <- gtrends(c("europska unija", "izbori za evropski parlament", "europski parlament"), geo = "HR", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Czech Republic
CZ14 <- gtrends(c("evropská unie", "volby do evropského parlamentu", "evropský parlament"), geo = "CZ", time = "2014-04-25 2014-05-25", low_search_volume =T)
CZ19 <- gtrends(c("evropská unie", "volby do evropského parlamentu", "evropský parlament"), geo = "CZ", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Denmark
DK14 <- gtrends(c("den europæiske union", "europa-parlamentsvalget", "europa-parlamentet"), geo = "DK", time = "2014-04-25 2014-05-25", low_search_volume =T)
DK19 <- gtrends(c("den europæiske union", "europa-parlamentsvalget", "europa-parlamentet"), geo = "DK", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Estonia
EE14 <- gtrends(c("euroopa liit", "euroopa parlamendi valimised", "euroopa parlament"), geo = "EE", time = "2014-04-25 2014-05-25", low_search_volume =T)
EE19 <- gtrends(c("euroopa liit", "euroopa parlamendi valimised", "euroopa parlament"), geo = "EE", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Finland
FI14 <- gtrends(c("euroopan unioni", "europarlamenttivaalit", "euroopan parlamentti"), geo = "FI", time = "2014-04-25 2014-05-25", low_search_volume =T)
FI19 <- gtrends(c("euroopan unioni", "europarlamenttivaalit", "euroopan parlamentti"), geo = "FI", time = "2019-04-26 2019-05-26", low_search_volume =T)

#France
FR14 <- gtrends(c("l’union européenne", "élections européennes", "parlement européen"), geo = "FR", time = "2014-04-25 2014-05-25", low_search_volume =T)
FR19 <- gtrends(c("l’union européenne", "élections européennes", "parlement européen"), geo = "FR", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Germany
DE14 <- gtrends(c("die europäische union", "europawahl", "europäisches parlament"), geo = "DE", time = "2014-04-25 2014-05-25", low_search_volume =T)
DE19 <- gtrends(c("die europäische union", "europawahl", "europäisches parlament"), geo = "DE", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Hungary
HU14 <- gtrends(c("az európai unió", "európai parlamenti választás", "európai parlament"), geo = "HU", time = "2014-04-25 2014-05-25", low_search_volume =T)
HU19 <- gtrends(c("az európai unió", "európai parlamenti választás", "európai parlament"), geo = "HU", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Ireland
IE14 <- gtrends(c("the european union", "european parliament election", "european parliament"), geo = "IE", time = "2014-04-25 2014-05-25", low_search_volume =T)
IE19 <- gtrends(c("the european union", "european parliament election", "european parliament"), geo = "IE", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Italy
IT14 <- gtrends(c("l’unione europea", "elezioni europee", "parlamento europeo"), geo = "IT", time = "2014-04-25 2014-05-25", low_search_volume =T)
IT19 <- gtrends(c("l’unione europea", "elezioni europee", "parlamento europeo"), geo = "IT", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Latvia
LV14 <- gtrends(c("eiropas savienība", "eiropas parlamenta vēlēšanas", "eiropas parlaments"), geo = "LV", time = "2014-04-25 2014-05-25", low_search_volume =T)
LV19 <- gtrends(c("eiropas savienība", "eiropas parlamenta vēlēšanas", "eiropas parlaments"), geo = "LV", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Luxembourg
LU14 <- gtrends(c("l’union européenne", "élections européennes", "parlement européen"), geo = "LU", time = "2014-04-25 2014-05-25", low_search_volume =T)
LU19 <- gtrends(c("l’union européenne", "élections européennes", "parlement européen"), geo = "LU", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Netherlands
NL14 <- gtrends(c("de europese unie", "europese parlementsverkiezingen", "europees parlement"), geo = "NL", time = "2014-04-25 2014-05-25", low_search_volume =T)
NL19 <- gtrends(c("de europese unie", "europese parlementsverkiezingen", "europees parlement"), geo = "NL", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Poland
PL14 <- gtrends(c("unia europejska", "wybory do parlamentu europejskiego", "parlament europejski"), geo = "PL", time = "2014-04-25 2014-05-25", low_search_volume =T)
PL19 <- gtrends(c("unia europejska", "wybory do parlamentu europejskiego", "parlament europejski"), geo = "PL", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Portugal
PT14 <- gtrends(c("a união europeia", "eleições parlamentares europeias", "parlamento europeu"), geo = "PT", time = "2014-04-25 2014-05-25", low_search_volume =T)
PT19 <- gtrends(c("a união europeia", "eleições parlamentares europeias", "parlamento europeu"), geo = "PT", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Romania
RO14 <- gtrends(c("uniunea europeană", "alegeri pentru parlamentul european", "parlamentul european"), geo = "RO", time = "2014-04-25 2014-05-25", low_search_volume =T)
RO19 <- gtrends(c("uniunea europeană", "alegeri pentru parlamentul european", "parlamentul european"), geo = "RO", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Slovakia
SK14 <- gtrends(c("európska únia", "voľby do európskeho parlamentu", "európsky parlament"), geo = "SK", time = "2014-04-25 2014-05-25", low_search_volume =T)
SK19 <- gtrends(c("európska únia", "voľby do európskeho parlamentu", "európsky parlament"), geo = "SK", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Slovenia
SI14 <- gtrends(c("evropska unija", "volitve v evropski parlament", "evropski parlament"), geo = "SI", time = "2014-04-25 2014-05-25", low_search_volume =T)
SI19 <- gtrends(c("evropska unija", "volitve v evropski parlament", "evropski parlament"), geo = "SI", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Spain
ES14 <- gtrends(c("la unión europea", "elecciones al parlamento europeo", "parlamento europeo"), geo = "ES", time = "2014-04-25 2014-05-25", low_search_volume =T)
ES19 <- gtrends(c("la unión europea", "elecciones al parlamento europeo", "parlamento europeo"), geo = "ES", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Sweden
SE14 <- gtrends(c("europeiska unionen", "europaparlamentsvalet", "europaparlamentet"), geo = "SE", time = "2014-04-25 2014-05-25", low_search_volume =T)
SE19 <- gtrends(c("europeiska unionen", "europaparlamentsvalet", "europaparlamentet"), geo = "SE", time = "2019-04-26 2019-05-26", low_search_volume =T)

#Great Britain
GB14 <- gtrends(c("the european union", "european parliament election", "european parliament"), geo = "GB", time = "2014-04-25 2014-05-25", low_search_volume =T)
GB19 <- gtrends(c("the european union", "european parliament election", "european parliament"), geo = "GB", time = "2019-04-26 2019-05-26", low_search_volume =T)

```


Computing of new gtrends variables that only include $interest over time.
Drop original gtrends objects.
```{r}
AT14IOT <- as_tibble(AT14$interest_over_time)
AT19IOT <- as_tibble(AT19$interest_over_time)

CZ14IOT <- as_tibble(CZ14$interest_over_time)
CZ19IOT <- as_tibble(CZ19$interest_over_time)

DE14IOT <- as_tibble(DE14$interest_over_time)
DE19IOT <- as_tibble(DE19$interest_over_time)

DK14IOT <- as_tibble(DK14$interest_over_time)
DK19IOT <- as_tibble(DK19$interest_over_time)

EE14IOT <- as_tibble(EE14$interest_over_time)
EE19IOT <- as_tibble(EE19$interest_over_time)

ES14IOT <- as_tibble(ES14$interest_over_time)
ES19IOT <- as_tibble(ES19$interest_over_time)

FI14IOT <- as_tibble(FI14$interest_over_time)
FI19IOT <- as_tibble(FI19$interest_over_time)

FR14IOT <- as_tibble(FR14$interest_over_time)
FR19IOT <- as_tibble(FR19$interest_over_time)

GB14IOT <- as_tibble(GB14$interest_over_time)
GB19IOT <- as_tibble(GB19$interest_over_time)

HR14IOT <- as_tibble(HR14$interest_over_time)
HR19IOT <- as_tibble(HR19$interest_over_time)

HU14IOT <- as_tibble(HU14$interest_over_time)
HU19IOT <- as_tibble(HU19$interest_over_time)

IE14IOT <- as_tibble(IE14$interest_over_time)
IE19IOT <- as_tibble(IE19$interest_over_time)

IT14IOT <- as_tibble(IT14$interest_over_time)
IT19IOT <- as_tibble(IT19$interest_over_time)

LU14IOT <- as_tibble(LU14$interest_over_time)
LU19IOT <- as_tibble(LU19$interest_over_time)

LV14IOT <- as_tibble(LV14$interest_over_time)
LV19IOT <- as_tibble(LV19$interest_over_time)

NL14IOT <- as_tibble(NL14$interest_over_time)
NL19IOT <- as_tibble(NL19$interest_over_time)

PL14IOT <- as_tibble(PL14$interest_over_time)
PL19IOT <- as_tibble(PL19$interest_over_time)

PT14IOT <- as_tibble(PT14$interest_over_time)
PT19IOT <- as_tibble(PT19$interest_over_time)

RO14IOT <- as_tibble(RO14$interest_over_time)
RO19IOT <- as_tibble(RO19$interest_over_time)

SE14IOT <- as_tibble(SE14$interest_over_time)
SE19IOT <- as_tibble(SE19$interest_over_time)

SI14IOT <- as_tibble(SI14$interest_over_time)
SI19IOT <- as_tibble(SI19$interest_over_time)

SK14IOT <- as_tibble(SK14$interest_over_time)
SK19IOT <- as_tibble(SK19$interest_over_time)

#Drop original GT-objects from environmnet (can easily be loaded again if need be)
remove(AT14, AT19, CZ14, CZ19, DE14, DE19, DK14, DK19, 
       EE14, EE19, ES14, ES19, FI14, FI19, FR14, FR19, 
       GB14, GB19, HR14, HR19, HU14, HU19, IE14, IE19, 
       IT14, IT19, LU14, LU19, LV14, LV19, NL14, NL19,
       PL14, PL19, PT14, PT19, RO14, RO19, SE14, SE19, 
       SI14, SI19, SK14, SK19)
```

Spread the three keywords for each IOT-object (created in R Script "Import of voter turnout")
```{r}
AT14IOT<- AT14IOT %>% 
  spread(key = keyword, value = hits)
AT19IOT <- AT19IOT %>% 
  spread(key = keyword, value = hits)

CZ14IOT <- CZ14IOT %>% 
  spread(key = keyword, value = hits)
CZ19IOT <- CZ19IOT %>% 
  spread(key = keyword, value = hits)

DE14IOT <- DE14IOT %>% 
  spread(key = keyword, value = hits)
DE19IOT <- DE19IOT %>% 
  spread(key = keyword, value = hits)

DK14IOT <- DK14IOT %>% 
  spread(key = keyword, value = hits)
DK19IOT <- DK19IOT %>% 
  spread(key = keyword, value = hits)

EE14IOT <- EE14IOT %>% 
  spread(key = keyword, value = hits)
EE19IOT <- EE19IOT %>% 
  spread(key = keyword, value = hits)

ES14IOT <- ES14IOT %>% 
  spread(key = keyword, value = hits)
ES19IOT <- ES19IOT %>% 
  spread(key = keyword, value = hits)

FI14IOT <- FI14IOT %>% 
  spread(key = keyword, value = hits)
FI19IOT <- FI19IOT %>% 
  spread(key = keyword, value = hits)

FR14IOT <- FR14IOT %>% 
  spread(key = keyword, value = hits)
FR19IOT <- FR19IOT %>% 
  spread(key = keyword, value = hits)

GB14IOT <- GB14IOT %>% 
  spread(key = keyword, value = hits)
GB19IOT <- GB19IOT %>% 
  spread(key = keyword, value = hits)

HR14IOT <- HR14IOT %>% 
  spread(key = keyword, value = hits)
HR19IOT <- HR19IOT %>% 
  spread(key = keyword, value = hits)

HU14IOT <- HU14IOT %>% 
  spread(key = keyword, value = hits)
HU19IOT <- HU19IOT %>% 
  spread(key = keyword, value = hits)

IE14IOT <- IE14IOT %>% 
  spread(key = keyword, value = hits)
IE19IOT <- IE19IOT %>% 
  spread(key = keyword, value = hits)

IT14IOT <- IT14IOT %>% 
  spread(key = keyword, value = hits)
IT19IOT <- IT19IOT %>% 
  spread(key = keyword, value = hits)

LU14IOT <- LU14IOT %>% 
  spread(key = keyword, value = hits)
LU19IOT <- LU19IOT %>% 
  spread(key = keyword, value = hits)

LV14IOT <- LV14IOT %>% 
  spread(key = keyword, value = hits)
LV19IOT <- LV19IOT %>% 
  spread(key = keyword, value = hits)

NL14IOT <- NL14IOT %>% 
  spread(key = keyword, value = hits)
NL19IOT <- NL19IOT %>% 
  spread(key = keyword, value = hits)

PL14IOT <- PL14IOT %>% 
  spread(key = keyword, value = hits)
PL19IOT <- PL19IOT %>% 
  spread(key = keyword, value = hits)

PT14IOT <- PT14IOT %>% 
  spread(key = keyword, value = hits)
PT19IOT <- PT19IOT %>% 
  spread(key = keyword, value = hits)

RO14IOT <- RO14IOT %>% 
  spread(key = keyword, value = hits)
RO19IOT <- RO19IOT %>% 
  spread(key = keyword, value = hits)

SE14IOT <- SE14IOT %>% 
  spread(key = keyword, value = hits)
SE19IOT <- SE19IOT %>% 
  spread(key = keyword, value = hits)

SI14IOT <- SI14IOT %>% 
  spread(key = keyword, value = hits)
SI19IOT <- SI19IOT %>% 
  spread(key = keyword, value = hits)

SK14IOT <- SK14IOT %>% 
  spread(key = keyword, value = hits)
SK19IOT <- SK19IOT %>% 
  spread(key = keyword, value = hits)

```

For consistency all unique keywords are renamed each IOT-object. 
This makes it possible to meaningfully combine the IOT-objects afterwards  

The new keyword names are as follows:
[1] "EU" #the european union 
[2] "Elec" #european parliament election
[3] "EP" #the european parliament

```{r}
AT14IOT<- AT14IOT %>% 
  dplyr::rename(EU = 'die europäische union', Elec = europawahl, EP = 'europäisches parlament')
AT19IOT <- AT19IOT %>% 
 dplyr::rename(EU = 'die europäische union', Elec = europawahl, EP = 'europäisches parlament')

CZ14IOT <- CZ14IOT %>% 
 dplyr::rename(EU = 'evropská unie', Elec = 'volby do evropského parlamentu', EP = 'evropský parlament')
CZ19IOT <- CZ19IOT %>% 
 dplyr::rename(EU = 'evropská unie', Elec = 'volby do evropského parlamentu', EP = 'evropský parlament')

DE14IOT <- DE14IOT %>% 
 dplyr::rename(EU = 'die europäische union', Elec = europawahl, EP = 'europäisches parlament')
DE19IOT <- DE19IOT %>% 
 dplyr::rename(EU = 'die europäische union', Elec = europawahl, EP = 'europäisches parlament')

DK14IOT <- DK14IOT %>% 
 dplyr::rename(EU = 'den europæiske union', Elec = 'europa-parlamentsvalget', EP = 'europa-parlamentet')
DK19IOT <- DK19IOT %>% 
  dplyr::rename(EU = 'den europæiske union', Elec = 'europa-parlamentsvalget', EP = 'europa-parlamentet')

EE14IOT <- EE14IOT %>% 
 dplyr::rename(EU = 'euroopa liit', Elec = 'euroopa parlamendi valimised', EP = 'euroopa parlament')
EE19IOT <- EE19IOT %>% 
 dplyr::rename(EU = 'euroopa liit', Elec = 'euroopa parlamendi valimised', EP = 'euroopa parlament')

ES14IOT <- ES14IOT %>% 
 dplyr::rename(EU = 'la unión europea', Elec = 'elecciones al parlamento europeo', EP = 'parlamento europeo')
ES19IOT <- ES19IOT %>% 
 dplyr::rename(EU = 'la unión europea', Elec = 'elecciones al parlamento europeo', EP = 'parlamento europeo')

FI14IOT <- FI14IOT %>% 
 dplyr::rename(EU = 'euroopan unioni', Elec = 'europarlamenttivaalit', EP = 'euroopan parlamentti')
FI19IOT <- FI19IOT %>% 
 dplyr::rename(EU = 'euroopan unioni', Elec = 'europarlamenttivaalit', EP = 'euroopan parlamentti')

FR14IOT <- FR14IOT %>% 
 dplyr::rename(EU = 'l’union européenne', Elec = 'élections européennes', EP = 'parlement européen')
FR19IOT <- FR19IOT %>% 
 dplyr::rename(EU = 'l’union européenne', Elec = 'élections européennes', EP = 'parlement européen')

GB14IOT <- GB14IOT %>% 
 dplyr::rename(EU = 'the european union', Elec = 'european parliament election', EP = 'european parliament')
GB19IOT <- GB19IOT %>% 
 dplyr::rename(EU = 'the european union', Elec = 'european parliament election', EP = 'european parliament')

HR14IOT <- HR14IOT %>% 
 dplyr::rename(EU = 'europska unija', Elec = 'izbori za evropski parlament', EP = 'europski parlament')
HR19IOT <- HR19IOT %>% 
 dplyr::rename(EU = 'europska unija', Elec = 'izbori za evropski parlament', EP = 'europski parlament')

HU14IOT <- HU14IOT %>% 
 dplyr::rename(EU = 'az európai unió', Elec = 'európai parlamenti választás', EP = 'európai parlament')
HU19IOT <- HU19IOT %>% 
 dplyr::rename(EU = 'az európai unió', Elec = 'európai parlamenti választás', EP = 'európai parlament')

IE14IOT <- IE14IOT %>% 
 dplyr::rename(EU = 'the european union', Elec = 'european parliament election', EP = 'european parliament')
IE19IOT <- IE19IOT %>% 
 dplyr::rename(EU = 'the european union', Elec = 'european parliament election', EP = 'european parliament')

IT14IOT <- IT14IOT %>% 
 dplyr::rename(EU = 'l’unione europea', Elec = 'elezioni europee', EP = 'parlamento europeo')
IT19IOT <- IT19IOT %>% 
 dplyr::rename(EU = 'l’unione europea', Elec = 'elezioni europee', EP = 'parlamento europeo')

LU14IOT <- LU14IOT %>% 
 dplyr::rename(EU = 'l’union européenne', Elec = 'élections européennes', EP = 'parlement européen')
LU19IOT <- LU19IOT %>% 
 dplyr::rename(EU = 'l’union européenne', Elec = 'élections européennes', EP = 'parlement européen')

LV14IOT <- LV14IOT %>% 
 dplyr::rename(EU = 'eiropas savienība', Elec = 'eiropas parlamenta vēlēšanas', EP = 'eiropas parlaments')
LV19IOT <- LV19IOT %>% 
 dplyr::rename(EU = 'eiropas savienība', Elec = 'eiropas parlamenta vēlēšanas', EP = 'eiropas parlaments')

NL14IOT <- NL14IOT %>% 
 dplyr::rename(EU = 'de europese unie', Elec = 'europese parlementsverkiezingen', EP = 'europees parlement')
NL19IOT <- NL19IOT %>% 
 dplyr::rename(EU = 'de europese unie', Elec = 'europese parlementsverkiezingen', EP = 'europees parlement')

PL14IOT <- PL14IOT %>% 
 dplyr::rename(EU = 'unia europejska', Elec = 'wybory do parlamentu europejskiego', EP = 'parlament europejski')
PL19IOT <- PL19IOT %>% 
 dplyr::rename(EU = 'unia europejska', Elec = 'wybory do parlamentu europejskiego', EP = 'parlament europejski')

PT14IOT <- PT14IOT %>% 
 dplyr::rename(EU = 'a união europeia', Elec = 'eleições parlamentares europeias', EP = 'parlamento europeu')
PT19IOT <- PT19IOT %>% 
 dplyr::rename(EU = 'a união europeia', Elec = 'eleições parlamentares europeias', EP = 'parlamento europeu')
 	
RO14IOT <- RO14IOT %>% 
 dplyr::rename(EU = 'uniunea europeană', Elec = 'alegeri pentru parlamentul european', EP = 'parlamentul european')
RO19IOT <- RO19IOT %>% 
 dplyr::rename(EU = 'uniunea europeană', Elec = 'alegeri pentru parlamentul european', EP = 'parlamentul european')

SE14IOT <- SE14IOT %>% 
 dplyr::rename(EU = 'europeiska unionen', Elec = 'europaparlamentsvalet', EP = 'europaparlamentet')
SE19IOT <- SE19IOT %>% 
 dplyr::rename(EU = 'europeiska unionen', Elec = 'europaparlamentsvalet', EP = 'europaparlamentet')

SI14IOT <- SI14IOT %>% 
 dplyr::rename(EU = 'evropska unija', Elec = 'volitve v evropski parlament', EP = 'evropski parlament')
SI19IOT <- SI19IOT %>% 
 dplyr::rename(EU = 'evropska unija', Elec = 'volitve v evropski parlament', EP = 'evropski parlament')

SK14IOT <- SK14IOT %>% 
 dplyr::rename(EU = 'európska únia', Elec = 'voľby do európskeho parlamentu', EP = 'európsky parlament')
SK19IOT <- SK19IOT %>% 
 dplyr::rename(EU = 'európska únia', Elec = 'voľby do európskeho parlamentu', EP = 'európsky parlament')
```

Merge IOT-objects into one dataset (GT) with rbind()

```{r}
GT <- 
  rbind(AT14IOT, AT19IOT, CZ14IOT, CZ19IOT, DE14IOT, DE19IOT, DK14IOT, DK19IOT, 
        EE14IOT, EE19IOT, ES14IOT, ES19IOT, FI14IOT, FI19IOT, FR14IOT, FR19IOT, 
        GB14IOT, GB19IOT, HR14IOT, HR19IOT, HU14IOT, HU19IOT, IE14IOT, IE19IOT, 
        IT14IOT, IT19IOT, LU14IOT, LU19IOT, LV14IOT, LV19IOT, NL14IOT, NL19IOT,
        PL14IOT, PL19IOT, PT14IOT, PT19IOT, RO14IOT, RO19IOT, SE14IOT, SE19IOT, 
        SI14IOT, SI19IOT, SK14IOT, SK19IOT)
```


#Preparation of new gtrends dataset

Transform Keyword variables to numeric, which will create NA's

```{r}
GT[, c(6:8)] <- sapply(GT[, c(6:8)], as.numeric) #transforms hits per keyword to numeric
```

Changing any new NA's to 0

```{r}
GT[is.na(GT)] = 0 
```

Two main things happen here:
 - The date variable is changed to date format
 - A dummy variable [0 = 2014, 1 = 2019] is computed  

The dummy is meant for later regression

```{r}
year(date(as.POSIXct("2014-04-25", format = "%Y-%m-%d")))
year(date(as.POSIXct("2019-04-26", format = "%Y-%m-%d")))

GT <- GT %>%
  mutate(year = year(date)) 
  
GT <- 
  dummy_cols(GT, select_columns = "year", remove_first_dummy = TRUE)
```


#Split-apply-combine aggregation of gtrends dataset

Summarization of the keyword data per country and year 

```{r}
GTsum <- GT %>%
 select(geo, year, year_2019, EU, Elec, EP) %>%
  group_by(geo, year_2019) %>%
  dplyr::summarise(
    mean_EU = mean(EU), median_EU = median(EU), variance_EU = var(EU), total_EU = sum(EU),
    mean_EP = mean(EP), median_EP = median(EP), variance_EP = var(EP), total_EP = sum(EP),
    mean_Elec = mean(Elec), median_Elec = median(Elec), variance_Elec = var(Elec), 
    total_Elec = sum(Elec)) %>%
  arrange(geo) %>% 
  as_tibble() 
```

Renaming of values in the new grouped variable - since 'geo' was not renamed earlier - so that each country abbrevation is changed with full country name.
This assures consistency for when the data will be merged with the VoterData (from earlier)

```{r}
GTsum[GTsum$geo == 'AT', "geo"] <- 'Austria'
GTsum[GTsum$geo == 'CZ', "geo"] <- 'Czech Republic'
GTsum[GTsum$geo == 'DE', "geo"] <- 'Germany'
GTsum[GTsum$geo == 'DK', "geo"] <- 'Denmark'
GTsum[GTsum$geo == 'EE', "geo"] <- 'Estonia'
GTsum[GTsum$geo == 'ES', "geo"] <- 'Spain'
GTsum[GTsum$geo == 'FI', "geo"] <- 'Finland'
GTsum[GTsum$geo == 'FR', "geo"] <- 'France'
GTsum[GTsum$geo == 'GB', "geo"] <- 'United Kingdom'
GTsum[GTsum$geo == 'HR', "geo"] <- 'Croatia'
GTsum[GTsum$geo == 'HU', "geo"] <- 'Hungary'
GTsum[GTsum$geo == 'IE', "geo"] <- 'Ireland'
GTsum[GTsum$geo == 'IT', "geo"] <- 'Italy'
GTsum[GTsum$geo == 'LU', "geo"] <- 'Luxembourg'
GTsum[GTsum$geo == 'LV', "geo"] <- 'Latvia'
GTsum[GTsum$geo == 'NL', "geo"] <- 'Netherlands'
GTsum[GTsum$geo == 'PL', "geo"] <- 'Poland'
GTsum[GTsum$geo == 'PT', "geo"] <- 'Portugal'
GTsum[GTsum$geo == 'RO', "geo"] <- 'Romania'
GTsum[GTsum$geo == 'SE', "geo"] <- 'Sweden'
GTsum[GTsum$geo == 'SI', "geo"] <- 'Slovenia'
GTsum[GTsum$geo == 'SK', "geo"] <- 'Slovakia'
```

Change the name of the actual variable from 'geo' to 'Country'
```{r}
GTsum <- GTsum %>% 
  rename(Country = 'geo')
```

#Regression analysis

First of all we have to merge the two datasets 'GTsum' and 'VoterDat1419' 
```{r}
VotesTrends <- 
  inner_join(GTsum, VoterDat1419, by = "Country")

glimpse(VotesTrends)
```


Here we rename Voter Turnout
```{r}
VotesTrends <- VotesTrends %>% 
  dplyr::rename(Voter_Turnout = 'Voter Turnout')
```


REGRESSION

MODEL 1
```{r}
m1 <- lm(Voter_Turnout ~ total_EP + total_EU + total_Elec + mean_EP +  mean_EU +  mean_Elec + median_EP + median_EU + median_Elec + variance_EP + variance_EU + variance_Elec + Country + year_2019 , data = VotesTrends)
summary(m1)
```

