---
title: "Predicting Voter Turnout with Google Trends"
subtitle: "Fundamentals of Computing and Data Display - Term Paper"
author: "Mathias Hector Schram"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r, include = FALSE}
# Her indgår de pakker, som skal loades for at man kan lave sin analyse
# include = FALSE betyder, at denne code chunk ikke indgår i PDF-outputtet


library(gtrendsR)
library(tidyverse)
library(data.table)
library(anytime)
library(tibbletime)
library(fastDummies)
library(lubridate)
library(scales)
library(mudata2)
library(lme4)
```

## Introduction

Since the first election for the European Parliament in 1979 voter turnout has been steadily declining. From 61.9 percent in the first election of 1979 to 42.6 percent in the election of 2014. However in the most recent European Parliament election voter turnout spiked with an increase to 50.6 percent. Why this was has to some extent already been answered by the EU itself: 2019 saw an increase amongst younger voters, and the environmental and economic situation as well contributed a great deal to that development^[https://www.europarl.europa.eu/news/en/press-room/20190923IPR61602/2019-european-elections-record-turnout-driven-by-young-people].

Since the 'why' has seemingly already been answered, this paper takes a step back and asks another question: Could we have predicted the surge in Voter Turnout? In this age of big data, Google Trends data  have been used to predict who would vote in the US for the 2008 and 2010 primaries [@Stephens-Davidowitz2013].  In this paper same fundamental thought is explored upon in an european context. Specifically the research question adressed in this paper is as follows:

Can Google Trends be used as a predictor for voter turnout?

To access and run this analysis, go to the GitHub repository, follow the hyperlink in the footnote^[https://github.com/mathias-hector/gtrends-term-paper].

## Data

The data used for this term paper comes from two different sources. First of all is the voter turnout data, which is downloaded from the International Institute for Democracy and Electoral Assistance (IDEA)^[https://www.idea.int/]. Second of all is the data from Google Trends that includes three keywords related to the election of the European Parliament (see codebook). 

Below is an example of an import of Google Trends data: 


```{r echo=TRUE}
library(gtrendsR)

#Austria
AT14 <- gtrends(c("die europäische union", "europawahl", "europäisches parlament"), geo = "AT", time = "2014-04-25 2014-05-25", low_search_volume =T)
AT19 <- gtrends(c("die europäische union", "europawahl", "europäisches parlament"), geo = "AT", time = "2019-04-26 2019-05-26", low_search_volume =T)

```

### Analysis and Discussion

With the research question in mind this section presents and discusses the main findings of the analysis. As is evident by the codebook, the main part of the data work has consisted of preparing the data in numerous ways for the final model. 

The final model is a multiple linear regression, which is computed from the code below: 

```{r echo=TRUE}
m1 <- lm(Voter_Turnout ~ total_EP + total_EU + total_Elec + mean_EP +  mean_EU +  mean_Elec + median_EP + median_EU + median_Elec + variance_EP + variance_EU + variance_Elec + Country + year_2019 , data = VotesTrends)
summary(m1)
```

From the model we gain a number of insights. With a Multiple R-squared of 0.8909, as well as a p-value that is < 0.0001, this first of all indicates that the model explains 89 percent of all the variability of the response data around its mean. Moreover it, the p-value, indicates what would normally be a rejection of the null-hypothesis. Therefore the overall conclusion of the term paper is that Google Trends can in fact be used as a predictor of voter turnout - at the very least for European Parliament elections. However one thing to note is the fact that Google Trends data in of itself can be tricky when it comes to making across-country comparisons. This follows from the normalization of Google Trends data that scales all keyword searches from 0 - 100. Moreover the necessity of using unique keywords for each country adds to the uncertainty of estimates.  


## References

Stephens-Davidowitz, Seth I., Using Google Data to Predict Who Will Vote (March 24, 2013). Available at SSRN: https://ssrn.com/abstract=2238863 or http://dx.doi.org/10.2139/ssrn.2238863