---
title: "Predicting Voter Turnout with Google Trends"
subtitle: "Fundamentals of Computing and Data Display - Term Paper"
author: "Mathias Hector Schram"
date: "`r Sys.Date()`"
output: 
   pdf_document:
     toc: yes
     df_print: kable
references:
  #GENERELT: SE paper-template fil - jeg tror, at JabRef eller Zotero skal bruges
  
---

```{r, include = FALSE}
# Her indgår de pakker, som skal loades for at man kan lave sin analyse
# include = FALSE betyder, at denne code chunk ikke indgår i PDF-outputtet

#install.packages("tibbletime")
#install.packages('fastDummies')
library(gtrendsR)
library(tidyverse)
library(data.table)
library(anytime)
library(tibbletime)
library(fastDummies)
library(lubridate)
library(scales)

#install.packages("mudata2")
library(mudata2)

#install.packages("broom")
#install.packages("modelr")
library(broom)
library(modelr)

library(lme4)

#install.packages("groupedstats")
library(groupedstats)

```

## Introduction

This section outlines the research idea. We can also cite related work here [@Wickham2014; @Baumer2017].

Note that compiled term paper (the PDF) is supposed to be more text-centered than the RMarkdown documents we used in class, i.e. the text sections are more detailed and big or redundant code chunks can be hidden.

LIGELEDES er det nice, at huske på, at selve paper-template bliver til en PDF på knap 1,5 sider - det er LUKSUS, da den afleverede rapport skal være 5-10 sider (og som enkelt person, må jeg godt være tættere på 5 end 10)

HUSK også at inkludere et link til GitHub - det kan passende være i introduktionen.

## Data

This section describes the data sources and the data gathering process.

```{r}
# A code chunk that exemplifies the data gathering process

```

```{r, include = FALSE}
# Additional code chunks that repeat tasks or do basic things can be hidden
```

## Results

This section presents the main results.

### Data exploration

The results section may have a data exploration part, but in general the structure here depends on the specific project.

```{r}
# What happens here depends on the specific project
```

```{r}
# What happens here depends on the specific project
```

### Analysis

This section presents the main results, such as (for example) stats and graphs that show relationships, model results and/or clustering, PCA, etc.

```{r}
# What happens here depends on the specific project
```

```{r}
# What happens here depends on the specific project
```

```{r}
# What happens here depends on the specific project
```

## Discussion

This section summarizes the results and may briefly outline advantages and limitations of the work presented.

## References